\curriculumvitae
Yasin Açıkmeşe was born in Mannheim/Germany on June 26, 1990. He studied at Kenan Evren Anatolian High School where he was graduated in 2008. He attended the undergraduate program of Manufacturing Systems/Industrial Engineering at Sabancı University. He received his B.S. degree in the Manufacturing Systems/Industrial Engineering in 2013. He worked at Akbank, Golive Consulting and Inovatink in the early years of the professional career. Now, he works at Tekkredi as a Data Scientist since October 2018 and continues to work towards a master’s degree in Logistics and Financial Management under the supervision of Assoc. Prof. Dr. Sadettin Emre Alptekin the Institute of Science and Engineering, Galatasaray University.

The papers that have appeared as full text in refereed proceedings of international conferences:

Acikmese, Y., Ustundag, B. C., & Golubovic, E. (2017, November). Towards an artificial training expert system for basketball. In 2017 10th International Conference on Electrical and Electronics Engineering (ELECO) (pp. 1300-1304). IEEE.

Uzunovic, T., Golubovic, E., Tucakovic, Z., Acikmese, Y., & Sabanovic, A. (2018, October). Task-Based Control and Human Activity Recognition for Human-Robot Collaboration. In IECON 2018-44th Annual Conference of the IEEE Industrial Electronics Society (pp. 5110-5115). IEEE.

The papers that accepted as full text in refereed proceedings of international conferences:

Acikmese, Y., Alptekin, S. E. (In Proceeding). Prediction of stress levels with LSTM and passive mobile sensors. In 2019 23rd International Conference on Knowledge-Based and Intelligent Information & Engineering
Systems (KES).

\label{chapter:vita}